A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex
moved tornado code to appendix

We were interested to calculate if the new implementation of dictionary can handle more requests in a Python web server compared to the current CPython implementation. We chose Tornado web server for this task since most of the code is written in pure Python. An instance of Tornado server was run in a virtual machine with one assigned processor. The following code[http://nichol.as/benchmark-of-python-web-servers] was used as a sample Tornado application:
 \begin{verbatim}
import tornado.httpserver
import tornado.ioloop
import tornado.wsgi

def application(environ, start_response):
    status = '200 OK'
    output = 'Pong!' 
    response_headers = [('Content-type', 'text/plain'),
        ('Content-Length', str(len(output)))]
    start_response(status, response_headers)
    return [output]
def main():
    container = tornado.wsgi.WSGIContainer(application)
    http_server = tornado.httpserver.HTTPServer(container)
    http_server.listen(8000)
    tornado.ioloop.IOLoop.instance().start()
if __name__ == "__main__":
    main()
 \end{verbatim}

@@

>>>>

We were interested to calculate if the new implementation of dictionary can handle more requests in a Python web server compared to the current CPython implementation. We chose Tornado web server for this task since most of the code is written in pure Python. An instance of Tornado server was run in a virtual machine with one assigned processor. The code of the application used is provided in the appendix.

@@

\appendix
\section{Tornado Application}
Sample Tornado 2.2.1 application used for benchmark:
 \begin{verbatim}
import tornado.httpserver
import tornado.ioloop
import tornado.wsgi

def application(environ, start_response):
    status = '200 OK'
    output = 'Hello World!' 
    response_headers = [('Content-type', 'text/plain'),
        ('Content-Length', str(len(output)))]
    start_response(status, response_headers)
    return [output]
def main():
    container = tornado.wsgi.WSGIContainer(application)
    http_server = tornado.httpserver.HTTPServer(container)
    http_server.listen(8000)
    tornado.ioloop.IOLoop.instance().start()
if __name__ == "__main__":
    main()
 \end{verbatim}
\appendix
